An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-11-30 latex-spie/article.tex
Introduction is almost finished

\begin{abstract}
Visual loop closure detection problem is an active area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors. In this paper, we propose an enhanced loop closure method based on unsupervised visual landmark extraction with saliency detection technique. In contradistinction to the previous methods, our approach uses additional depth information. Saliency regions are used to refer to the certain distinctive areas on the image patches. They are also suitable to represent locations in a sparse manner.  In order to find out the similarity between two locations we use a straightforward function, that contains the detection confidences of the image and the landmark coordinates in 3D. Recognition of the previously visited and unvisited locations is also considered in the framework. Exemplary results and the practical implementation of the method are also given with the data gathered on the testbed with a depth camera (Kinect) mounted differential drive autonomous ground vehicle. Specifically, we adopt visual place recognition to close loops that is useful for the process of correctly identifying a previously visited location. 
\end{abstract}

@@

In mobile robotics, autonomous navigation is an active research area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors. One of the major problems connected to robotic navigation is Simultaneous localization and mapping (SLAM) which still remains as an assertive problem in a lot of ways. Loop closing is defined as the correct identification of previously visited location in terms of SLAM. Information that is gathered from various data sources including LIDARs, RADARs, stereo       and monocular cameras is highly utilized in loop closure detection. With the recent development of visual sensor technologies, the loop closure detection became a problem that is open for research in the field of computer vision.

@@

\subsection{Literature Review}

Visual loop closing techniques can be categorized into three main parts\cite{Williams09} : Image-to-image and image-to-map, map-to-map techniques. Most of the image-to-image loop closing approaches that rely on considering whole image\cite{Cadena10, Cummins08} .

Loop closure estimations are cast by matching images. Most of image-to-image loop closing approaches that rely on salient image regions, utilize small, low-level features like \cite{springerlink:10.1007/11744023_32} extracted from the whole image \cite{4633680, CumminsNewmanIJRR08, 5650234, HoNewmanCIRA2005}. However, there is a technique that is used to extract relatively larger patches specific to environment that the robot navigates \cite{sariyanidi_iv} on. Similar approaches are defined in other studies as well\cite{Espinace:2008:UIU:1377036.1377148, 1570189}, however these techniques do not define a complete loop closing framework.

The Bag of Words\cite{1238663} method has also been widely used to visual place recognition. Many notable techniques have been developed after this representation, since it is quite suitable to represent place images and match them on an appearance space. The well-known FAB-MAP method proposes a generative probabilistic model\cite{CumminsNewmanIJRR08} which relies on BoW model, and a method to identify new places is proposed. The BoW model has also been utilized along with Bayesian Filtering\cite{4633680} to reliably detect the loop closures. The BoW model has also used to eliminate the majority of candidates\cite{5650234} and loop closing is decided after geometrically inconsistent matches are discarded using conditional random fields. More extensive information related visual loop closure techniques can be found on the relevant survey \cite{williams09}.

>>>>

\begin{abstract}
Visual loop closure detection problem is an active area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors. In this paper, we propose an enhanced loop closure method based on unsupervised visual landmark extraction with saliency detection technique. In contradistinction to the previous methods, our approach uses additional depth information. Saliency regions are used to refer to the certain distinctive areas on the image patches. They are also suitable to represent locations in a sparse manner.  In order to find out the similarity between two locations we use a straightforward function, that contains the detection confidences of the image and the landmark coordinates in 3D. Recognition of the previously visited and unvisited locations is also considered in the framework. Exemplary results and the practical implementation of the method are also given with the data gathered on the testbed with a depth camera (Kinect) mounted differential drive autonomous ground vehicle. Specifically, we adopt visual place recognition to close loops that is useful for the process of correctly identifying a previously visited location. The algorithm is tested in three different datasets which lighting conditions are different from each other. Additional depth information beside the actual image increases the detection rate especially in dark. 
\end{abstract}

@@

In mobile robotics, autonomous navigation is an active research area especially for the indoor environments, where the global position information is missing and the localization information is highly dependent on odometry sensors. One of the major problems connected to robotic navigation is Simultaneous localization and mapping (SLAM)\cite{CumminsNewmanIJRR08} which still remains as an assertive problem in a lot of ways. Loop closing is defined as the correct identification of previously visited location in terms of SLAM. Information that is gathered from various data sources including LIDARs, RADARs, stereo and monocular cameras\cite{williams08iros, 5650234} is highly utilized in loop closure detection. With the recent development of visual sensor technologies, the loop closure detection became a problem that is open for research in the field of computer vision.

Visual loop closing techniques can be categorized into three main parts\cite{Williams09}: Image-to-image and image-to-map, map-to-map techniques. Loop closure estimations\cite{sariyanidi_spie13}  are cast by matching images. Most of image-to-image techniques that rely on salient image patches, used small, low-level features such as \cite{springerlink:10.1007/11744023_32} extracted from the whole image \cite{sariyanidi_iv, HoNewmanCIRA2005}. One of the widely used methods in visual place recognition problem is the Bag of Words\cite{1238663} method. More information related to visual loop closing approaches can be found on the relevant survey \cite{Williams09}.

@@

In the next sections, a brief introduction about the methodology is explained first. After that, the experiments and datasets are shown, and finally results are presented.
